---
title: "SRT411A0"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---
This assignment was uploaded to github under username jthegrey. This assignment is basically to help understand the basics of R, as well as figure out how to use knitr to generate PDF's of the .Rmd file. 

I followed this guide: https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf


## 3.1 Calculator
The percetage of my life I have spent at Seneca. Note: for this section the guide said to use 2014, but since the year is 2018 I used that number instead.
```{r}
((2018 - 2017) / (2018 - 1993)) *100 
```

## 3.2 Workspace
Same as above, but used some variables.
```{r}
age = 2018 - 1993
years_in_school = 2018 - 2017
years_in_school/age * 100
```

## 3.4 Functions
Compute the sum of 4, 5, 8 and 11 by first combining  them  into  a  vector  and  then  using  the function sum.
```{r}
nums = c(4,5,8,11)
sum(nums)
```
## 3.5 Plots
Plot 100 normal random numbers
```{r}
plot_nums = rnorm(100)
plot(plot_nums)
```
## 4.0 Help Documentation
Find help for the sqrt function.
```{r}
help(sqrt)
```
## 5.0 Scripts
Script contents of firstscript.R:
plot_nums = rnorm(100)
plot(plot_nums)
```{r}
setwd("C:\\Users\\Hagop\\Desktop")
source("firstscript.R")
source("firstscript.R")
source("firstscript.R")
```
## 6.2 Matrices
Put  the  numbers  31  to  60  in  a  vector  named P and in a matrix with 6 rows and 5 columns named Q
```{r}
nums = seq(from=31, to=60, by=1)
mat = matrix(data=nums, ncol=5)
mat
```
## 6.3 Data Frames
Make  a  script  file  which  constructs  three  random  normal  vectors  of  length  100.   Call  these vectors x1,x2 andx3. Make a data frame called t with three columns (called a , b and c) containing  respectively x1, x1+x2 and x1+x2+x3. Call the following functions for this data frame: plot(t) and sd(t).

```{r}
x1=rnorm(100)
x2=rnorm(100)
x3=rnorm(100)
t= data.frame(a = x1, b= (x1+x2), c=(x1+x2+x3))
plot(t)
```

sd(t) fails, so it was omitted.

## 7.0 Graphics

```{r}
x1=rnorm(100)
x2=rnorm(100)
x3=rnorm(100)
t= data.frame(a = x1, b= (x1+x2), c=(x1+x2+x3))

plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4, col=rgb(0,0,1,0.3))
```
## 8.0 Reading and writing data files

```{r}
data1=read.table(file="tst1.txt", header=TRUE)
data1
data1[2] * 5
write.table(data1,file="tst1.txt",row.names=FALSE)
data1
```
## 9.0 Not Available Data

```{r}
mean(sqrt(rnorm(100)),na.rm =TRUE)
```

This section creates an error because the sqrt of negative numbers does not exist, this leaves holes in the data. We used na.rm=TRUE to tell the interpreter to ignore the missing data.

## 10.0 Classes
Make  a  graph  with  on  the  x-axis:  today,  Sinterklaas  2014  and  your  next  birthday  and  on the y-axis the number of presents you expect on each of these days
```{r}
dates=strptime(c("20180216042200", "20141225010000", "20181024010000"), format="%Y%m%d%H%M%S")
gifts = c(12, 85, 99)
plot(dates,gifts)
```



## 11.2 For-Loop

```{r}
s =c()
for(i in 1:100)
{
  if (i < 5 | i >90)
  {
    s[i] = (i *10)
  }
  else
  {
    s[i]= i * 0.1
  }
}
s

```

## 11.3 Writing your own Functions

```{r}
fun1 = function(arg1)
{
  s=c()
for(i in 1:length(arg1))
{
  if (i < 5 | i >90)
  {
    s[i] = (i *10)
  }
  else
  {
    s[i]= i * 0.1
  }
}
s
}

fun1(arg1=seq(from=1, to=100, by=1))

```


## Extra ToDo in Footnote

```{r}
fun1 = function(arg1)
{
less = arg1[ arg1 <=5 | arg1 >= 90] * 5
mid = arg1[ arg1 >=5 | arg1 <= 90] * 0.1 
arg1 <- c(less,mid)
}

fun1(arg1=seq(from=1, to=100, by=1))
```

Sources used:

https://nicercode.github.io/guides/reports/
https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf
https://www.dataquest.io/blog/how-to-share-data-science-portfolio/


